\bf $\mathsf{TEDAT}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-20 paper.tex
tables

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{TEDAT}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$c_e$ &\multicolumn{6}{|l}{the remaining capacity on link $e \in E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(estination) pair in s-d pair set}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
\hline
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\multirow{3}{*}{$d_i=(\mathbf{b_i}, \beta_i)$}&\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{b}_i^1, \mathbf{b}_i^2, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}} \\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
\hline
$D, D_a$ &\multicolumn{6}{|l}{the set of arrived demands and admitted demands}\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$d_{ik}$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$\bm{z}\in \bm{Z}$ &\multicolumn{6}{|l}{a failure scenario in the scenario set}\\
\hline
$p_{\bm{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\bm{z}$ occurs}\\
\hline
$v_t^{\bm{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\bm{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

&\textbf{Output Variables}\\
\hline
$g_i$& \multicolumn{6}{|l}{whether demand $i$ is admitted}\\
\hline
%$f_{ikt}$& \multicolumn{6}{|l}{bandwidth allocated for the $i$-th demand over tunnel $t \in T_{k}$ }\\
$f_i^t$& \multicolumn{6}{|l}{bandwidth allocated for demand $i$ over tunnel $t$}\\
\hline
$h_i$& \multicolumn{6}{|l}{profit (after refunding)  for demand $i$}\\
%\hline
%\hline
%&\textbf{Auxiliary Output Variables}\\
%\hline
%% $S_j$ &\multicolumn{6}{|l}{Network service achieved availability of $j$}\\
%%\hline
% $A_i(\bm{z})$&\multicolumn{6}{|l}{Whether scenario $\bm{z}$ is safe or not for $i$ }\\
% \hline
% $S_i$&\multicolumn{6}{|l}{Achieved availability of $i$ }\\
\bottomrule
\bottomrule
\end{tabular}
\end{table}

>>>>

\begin{table}[h!]
\small
\centering
\caption{Key Notations for $\mathsf{TEDAT}$}\label{Notation}
\renewcommand{\arraystretch}{1.0}
\begin{tabular}{ccccccc}  \toprule \toprule 
\setlength{\tabcolsep}{5pt}
&\textbf{Input Variables}\\
\hline
$G(V,E)$ &\multicolumn{6}{|l}{inter-DC WAN with nodes $V$ and Links $E$}\\
\hline
$c_e$ &\multicolumn{6}{|l}{the remaining capacity on link $e \in E$}\\
\hline
$k\in K$ &\multicolumn{6}{|l}{a s(ource)-d(estination) pair in s-d pair set}\\
\hline
$T_{k}$ &\multicolumn{6}{|l}{the set of tunnels for a s-d pair $k$}\\
\hline
%\multirow{3}{*}{VM Instances}&\multicolumn{2}{|c|}{$< 99.99\%$}&\multicolumn{2}{|c|}{$10\%$}&\multirow{3}{*}{Azure}\\
%&\multicolumn{2}{|c|}{$< 99\%$}&\multicolumn{2}{|c|}{25\%}& \\
%&\multicolumn{2}{|c|}{$< 95\%$}&\multicolumn{2}{|c|}{100\%}& \\
\multirow{3}{*}{$d_i=(\mathbf{b_i}, \beta_i)$}&\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with }\\
&\multicolumn{6}{|l}{ availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{b}_i^1, \mathbf{b}_i^2, ...>$}\\
&\multicolumn{6}{|l}{of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and traffic scheduling.}} \\
%$d_i=(\mathbf{b_i}, \beta_i)$ &\multicolumn{6}{|l}{the $i$-th user demand, requiring bandwidth $\mathbf{b_i}$ with availability $\beta_i$, where $\mathbf{b_i}$ is a vector $<\mathbf{d}_i^1, \mathbf{d}_i^2, ...>$ of bandwidth demands over all s-d pairs\footnote{Here we omit the start and end time of this demand, but they will be implicitly considered in our online admission and scheduling.}}\\
\hline
$D, D_a$ &\multicolumn{6}{|l}{the set of arrived demands and admitted demands}\\
%\hline
% $j\in J$ &\multicolumn{6}{|l}{the $j$-th availability target in the level set}\\
%\hline
%$d_{ik}$ &\multicolumn{6}{|l}{Bandwidth demand through node pair $k$ of $i$}\\
%\hline
%$\gamma_{i}$ &\multicolumn{6}{|l}{Service type (i.e., $j$) of demand $i$}\\
%\hline
%$ \beta_{j}$ &\multicolumn{6}{|l}{Bandwidth-based availability target of service $j$}\\
\hline
$t$ &\multicolumn{6}{|l}{a tunnel for transmitting traffic\footnote{Multiple tunnels may exist for a single s-d pair.}}\\
\hline
$u_t^e$ &\multicolumn{6}{|l}{whether tunnel $t$ passes link $e \in E$}\\
\hline
$\bm{z}\in \bm{Z}$ &\multicolumn{6}{|l}{a failure scenario in the scenario set}\\
\hline
$p_{\bm{z}}$ &\multicolumn{6}{|l}{the probability that a failure scenario $\bm{z}$ occurs}\\
\hline
$v_t^{\bm{z}}$ &\multicolumn{6}{|l}{whether tunnel $t$ is available under scenario $\bm{z}$}\\
 \hline
% $\{1,\beta_j^1,\beta_j^2....\}$ &\multicolumn{6}{|l}{The availability target list for service $j$}\\
%  \hline
% $\{1,\alpha_j^1,\alpha_j^2...\}$ &\multicolumn{6}{|l}{The profit list for service $j$}\\
\hline

&\textbf{Output Variables}\\
\hline
$g_d$& \multicolumn{6}{|l}{whether demand $d$ is admitted}\\
\hline
%$f_{ikt}$& \multicolumn{6}{|l}{bandwidth allocated for the $i$-th demand over tunnel $t \in T_{k}$ }\\
$f_d^t$& \multicolumn{6}{|l}{bandwidth allocated for demand $d$ over tunnel $t$}\\
\hline
$h_d$& \multicolumn{6}{|l}{profit (after refunding)  for demand $d$}\\
%\hline
%\hline
%&\textbf{Auxiliary Output Variables}\\
%\hline
%% $S_j$ &\multicolumn{6}{|l}{Network service achieved availability of $j$}\\
%%\hline
% $A_i(\bm{z})$&\multicolumn{6}{|l}{Whether scenario $\bm{z}$ is safe or not for $i$ }\\
% \hline
% $S_i$&\multicolumn{6}{|l}{Achieved availability of $i$ }\\
\bottomrule
\bottomrule
\end{tabular}
\end{table}
